Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-01-07 PaperVictor.tex
Revise abstr

Photonic crystal (PC)-based \notaL{Lo cambié de PhC, pues en otros
  casos abrevias photonic con sólo la P, como en PBG, no PhBG.}
structures have been extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
are consequently organized into photonic bands. Analogous to electrons in a
crystal, their propagation will be forbidden if their energy lies
within certain regions known as photonic band gaps (PBG's). Thus, the
PC behaves as a mirror if illuminated by light with frequencies
withinin a PBG. For several applications it is useful to fabricate
{\em ommnidirectional} mirrors with a wide band gap.  The use of metallic
mirrors is limited due to their relatively large absorption at
visible and near infrared frequencies.  An attractive alternative
consists of low-absorption dielectric
structures,  which may be designed for specific frequency
ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
of periodically alternating
layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
thicknesses of is quarter-wavelength
$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at some chosen nominal
wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
and the number of periods are large enough. Mirrors with high
reflectance within a wider frequency range may be engineered by
using different nominal wavelengths for different layers.
One way to obtain such structures is to gradually change the width of
the layers as a function of their depth, producing
\textit{chirped}-type \cite{Zipock1997}
structures. An alternative is to stack BM's, such that their PBG
overlap each other, resulting in a wider high-reflection band
\cite{Xifre2009}.
\notaL{No me convence la redacción. ¿No la revisó Vivechna?} \notaL{Para un
  espejo de Bragg, el ancho de banda de reflexión coincide (a incidencia normal)
  con la brecha prohibida, pero para los 'chirped' y los 'stacked',
  que no son periódicos, tal vez 'brecha prohibida' no es un buen
  término. Más bien, queremos hablar del ancho de banda del espejo,
  i.e., la región en que es buen reflector.}

Till now, different deposition techniques have been used to obtain omnidirectional
BM (ODBM) that operate on the visible and near infrared (Vis-NIR) range of the
electromagnetic spectrum. For example, Chen et al. \cite{Chen1999},
\notaL{Hay que checar que la puntuación vaya después de las citas,
  para este estilo de citas entre corchetes} \notaV{Comentario atendido} have
reported an ODBM of about 70 nm in the NIR range with 6-pairs  of
TiO$_{2}$/SiO$_{2}$ layers deposited with a sol-gel method. Park et al. \cite{Park2003},
used molecular beam epitaxy to grow a stack of four pairs of GaAs/AlAs layers,
followed by its conversion to
GaAs/Al$_{2}$O$_{3}$ layers by selective
oxidation of the AlAs layers, to obtain an ODBM with a band from 710 to 950
nm. On the other hand, DeCorby et al. \cite{DeCorby2005}, fabricated mirrors by
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide polymer, deposited by thermal evaporation and spin-casting
respectively, to obtain a 150 nm wide omnidirectional band centered at
1750 nm. Furthermore, Jena et al. \cite{Jena2019},
used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
_{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
layers) to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved ODBM from
592 to 668 nm. However, these techniques are expensive and they
require sophisticated equipment and long fabrication times. Using PS
is an attractive alternative, as PS may be fabricated by simple
electrochemical etching during short times of
crystalline Si in a hydrofluoric acid based electrolyte, to obtain the
sponge-like nanostructure composed of Si and air. By modulating in
time the applied current, the porosity of the PS, and thus its
refractive index, can be modulated
along its depth. This allows the design and fabrication of 1D-PC's with PS, to
control the propagation of light in a dielectric medium. The low cost and
ease of fabrication of PS make it an excellent candidate to develop
multilayered optical devices \cite{Xifre2015,Pavesi2000}.
Although optical filters \cite{Estevez2009,Ariza2014} are the most common
application of PS PC's, they have also been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
for photoluminescence control \cite{Antunez2014}. Recently, the study of
quasi-omnidirectional Bragg mirrors has
increased due to their possible application
as a flat lens \cite{Kozar2017,Cheng2018}.\notaL{Lens o mirror, no
  puede ser ambas? De verdad esto es lo que más lo ha popularizado?}
PS based dielectric
optical filters, quasi-ODBM and ODBM have been extensively studied in different
regions of the electromagnetic spectrum, such as the ultraviolet (UV)
\cite{Jimenez2020}, visible \cite{Ariza2012}, and (NIR)
\cite{Bruyant2003}. However, to obtain the desirable high index of refraction
contrast, layers of high porosity have to be employed, so that the
resulting structures may be fragile, making large structures, with a
very large number of layers, unfeasible. For this reason, in this work
we study different strategies to produce photonic mirrors
that have a large reflectance over a wide band-width with a relatively
small thickness and refractive index contrast. Specifically, our aim
is to maximize the reflectance $R$ averaged over a wide range of
wavelengths $\lambda$ and angles of incidence $\theta$.

>>>>

Photonic crystal (PC)-based \notaL{Lo cambié de PhC, pues en otros
  casos abrevias photonic con sólo la P, como en PBG, no PhBG.}
structures have been extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
are consequently organized into photonic bands. Analogous to electrons in a
crystal, their propagation is \notaV{Quite "will be"} forbidden if their energy lies
within certain regions known as photonic band gaps (PBG's). Thus, the
PC behaves as a mirror if illuminated by light with frequencies
withinin a PBG. For several applications it is useful to fabricate
{\em ommnidirectional} mirrors with a wide band gap.  The use of metallic
mirrors is limited due to their relatively large absorption at
visible and near infrared frequencies.  An attractive alternative
consists of low-absorption dielectric
structures,  which may be designed for specific frequency
ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
of periodically alternating
layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
thicknesses are \notaV{Modifique "of is"} quarter-wavelength
$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a \notaV{Quite "some chosen"} nominal
wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
and the number of periods are large enough. Mirrors with high
reflectance within a wider frequency range may be engineered by
using different nominal wavelengths for different layers.
One way to obtain such structures is to gradually change the width of
the layers as a function of their depth, producing
\textit{chirped}-type structures \cite{Zipock1997}.
Another alternative is to stack BMs, in such a way that their reflection bands partially
overlap each other at the edge, resulting in a wider high-reflection band \cite{Xifre2009}.
\notaV{Se modifico la oracion "An alternative is to stack BM's, such that their PBG
overlap each other, resulting in a wider high-reflection band"}. 
\notaL{No me convence la redacción. ¿No la revisó Vivechna?} \notaL{Para un
  espejo de Bragg, el ancho de banda de reflexión coincide (a incidencia normal)
  con la brecha prohibida, pero para los 'chirped' y los 'stacked',
  que no son periódicos, tal vez 'brecha prohibida' no es un buen
  término. Más bien, queremos hablar del ancho de banda del espejo,
  i.e., la región en que es buen reflector.}

On the other hand, different fabrication techniques have been used to obtain omnidirectional
mirrors (ODM) that operate on the visible and/or near infrared (Vis-NIR) range of the
electromagnetic spectrum. \notaV{Se modifico la oracion "Till now, different deposition 
techniques have been used to obtain omnidirectional BM (ODBM) that operate on 
the visible and near infrared (Vis-NIR) range of the electromagnetic spectrum."} 
For example, Chen et al. \cite{Chen1999},
\notaL{Hay que checar que la puntuación vaya después de las citas,
  para este estilo de citas entre corchetes} reported the fabrication of a 
6-pair TiO$_{2}$/SiO$_{2}$ structure \notaV{Se cambio "have reported"} with
 an OD band of about 70 nm in the NIR range, employing sol-gel deposition 
method. Park et al. \cite{Park2003}, used molecular beam epitaxy to 
grow a stack of four pairs of GaAs/AlAs layers, followed by its conversion to
GaAs/Al$_{2}$O$_{3}$ layers by selective oxidation of the AlAs 
layers, to obtain an OD with a band from 710 to 950 nm. 
On the other hand, DeCorby et al. \cite{DeCorby2005}, fabricated mirrors by
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide polymer, deposited by thermal evaporation and spin-casting
respectively, to obtain a 150 nm wide omnidirectional band centered at
1750 nm. Furthermore, Jena et al. \cite{Jena2019},
used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
_{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
layers) to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved an OD band from
592 to 668 nm. However, these techniques are expensive and they
require sophisticated equipment and long fabrication times. Using PS
is an attractive alternative, since it can be easily manufactured by 
electrochemical etching of crystalline Si in a hydrofluoric 
acid based electrolyte, to obtain a sponge-like nanostructure composed 
of Si and air. By modulating the supplied current and its application 
time to the electrochemical reaction, it is possible to obtain 
multilayer structures allowing for fabrication ODM \cite{Xifre2015,Pavesi2000}.
\notaV{Se replanteo la idea "as PS may be fabricated by simple
electrochemical etching during short times of
crystalline Si in a hydrofluoric acid based electrolyte, to obtain the
sponge-like nanostructure composed of Si and air. By modulating in
time the applied current, the porosity of the PS, and thus its
refractive index, can be modulated
along its depth. This allows the design and fabrication of 1D-PC's with PS, to
control the propagation of light in a dielectric medium. The low cost and
ease of fabrication of PS make it an excellent candidate to develop
multilayered optical devices."}
Although optical filters \cite{Estevez2009,Ariza2014} are the most common
application of PS PC's, they have also been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
for photoluminescence control \cite{Antunez2014}. Recently, the study of
chirped multilayer structures \notaV{Modifique "quasi-omnidirectional Bragg mirrors"} has
increased due to their possible application as flat focusing mirrors \cite{Wu2021,Kozar2017,Cheng2018}.
\notaL{Lens o mirror, no puede ser ambas? De verdad esto es lo que más lo ha popularizado?} 
PS based dielectric optical filters, quasi-ODBM and ODBM have been extensively studied in different
regions of the electromagnetic spectrum, such as the ultraviolet (UV)
\cite{Jimenez2020}, visible \cite{Ariza2012}, and NIR \cite{Bruyant2003}. 
However, to obtain the desirable high index of refraction
contrast, layers of high porosity have to be employed, so that the
resulting structures may be fragile, making large structures, with a
very large number of layers, unfeasible. For this reason, in this work
we study different strategies to produce multilayer \notaV{photonic} mirrors
that have a large reflectance omnidirectional band \notaV{over a wide band-width}
with relatively small thickness and refractive index contrast. 
\notaV{Se omite la frase "Specifically, our aim is to maximize the 
reflectance $R$ averaged over a wide range of wavelengths $\lambda$ 
and angles of incidence $\theta$", la idea general esta en la oracion anterior}
